The Evolution of Phenotypically Invariant Genetic Networks

### 2017-10-03 kalman_walk_paper.tex
edited envelope calc

%If the strength of selection is only a few multiples $\xi_1$ of the standing phenotypic diversity within a population $\sigma_S$, such that $\beta = \xi_1 \sigma_S$, and recombination load constrains the standing phenotype-neutral diversity $\sigma_N$ to be only a few multiples $\xi_2$ of $\sigma_S$, then $F_2$ fitness drop will be,
%  \begin{align}
%    \exp\left(- \xi^{2} \frac{T}{N_e} \right)
%  \end{align}
%  where $\xi := 2\xi_2/\xi_1$.
  If we assume that perpendicular variation segregating within a population is constrained by selection such that $\sigma_S/\gamma = \xi$, and that neutral variation is on the order of perpendicular variation, such that $\sigma_N = \sigma_S$, then the typical distance between two individuals drawn from separate allopatric populations will be $z = 2 \sigma_N \sqrt{T/N_e}$. We will expect a drop in hybrid fitness to be,
  \begin{align}
  \fit_2/\fit_0 = \exp \left(- 4\xi^2 \frac{T}{N_e} \right) .
  \end{align}
  Hybrid fitness depression will be significant when $z > \gamma$. 
  If $\xi$ is in $[\sfrac{1}{5},1]$, speciation will occur on the order of $N_e$ generations, and possibly much faster. Note, however, that if intrapopulation variation is very small such that $\sigma_S \ll \gamma$, speciation rates will be slower.
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
%
%\jss{Discussion guidelines:
%\begin{itemize}
%    \item Why is this important/useful?
%    \item What are the assumptions and shortcomings of the research?
%    \item Compare to other studies in the literature. 
%    \item Future directions. 
%    \item Wild speculations?
%    \item Conclusion and overall impact. 
%\end{itemize}}
%
The complexity of biological systems has limited our understanding of their function and evolution. Above we outline an approach, a first step, towards untangling this complexity in reference to function and evolution. This methodology borrows successfully applied tools from engineering and aims to synthesize these with the concepts and tools of molecular and evolutionary biology.

>>>>

%If the strength of selection is only a few multiples $\xi_1$ of the standing phenotypic diversity within a population $\sigma_S$, such that $\beta = \xi_1 \sigma_S$, and recombination load constrains the standing phenotype-neutral diversity $\sigma_N$ to be only a few multiples $\xi_2$ of $\sigma_S$, then $F_2$ fitness drop will be,
%  \begin{align}
%    \exp\left(- \xi^{2} \frac{T}{N_e} \right)
%  \end{align}
%  where $\xi := 2\xi_2/\xi_1$.
  Assume that perpendicular variation segregating within a population is constrained by selection such that $\sigma_S/\gamma = \xi$, and that neutral variation is on the order of perpendicular variation, such that $\sigma_N = \sigma_S$. Since the typical distance between two individuals drawn from separate allopatric populations will be $z = 2 \sigma_N \sqrt{T/N_e}$, we expect a drop in hybrid fitness of
  \begin{align}
  \fit_2/\fit_0 = \exp \left(- 4\xi^2 \frac{T}{N_e} \right) .
  \end{align}
  Hybrid fitness depression will be significant when $z > \gamma$. 
  If $\xi$ is in $[\sfrac{1}{5},1]$, speciation will occur on the order of $N_e$ generations, and possibly much faster. Note, however, that if intrapopulation variation is very small such that $\sigma_S \ll \gamma$, speciation rates will be slower.
%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
%
%\jss{Discussion guidelines:
%\begin{itemize}
%    \item Why is this important/useful?
%    \item What are the assumptions and shortcomings of the research?
%    \item Compare to other studies in the literature. 
%    \item Future directions. 
%    \item Wild speculations?
%    \item Conclusion and overall impact. 
%\end{itemize}}
%
The complexity of biological systems has limited our understanding of their function and evolution. Above we outline an approach, a first step, towards untangling this complexity in reference to function and evolution. This methodology borrows successfully applied tools from engineering and aims to synthesize these with the concepts and tools of molecular and evolutionary biology.
